The Evolution of Phenotypically Invariant Genetic Networks

### 2017-11-20 kalman_walk_paper.tex
discussion edits

If system drift induced hybrid breakdown occurs as rapidly as our model sugests, even in the absence of postive Darwinian selection, this would imply that species originate not necessarily by means of natural selection \citep{darwin1859origin}. While the incompatibility of any one given network within an organism may be small, we note that organsisms are made up of many different networks, and that the cumulative impact of system drift across all of these may be substantial. Further, even in populations experiencing directional selection, networks underlying conserved parts of the phenotype can still experience neutral drift and harbor incompatibilities. 
Our results show that hybrids, under neutral processes, break down as a function of genetic distance, and despite the present model's myriad simplifications and assumptions, 
it may, in part, explain the observed broad patterns of reproductive isolation among diverse phyla \citep{roux2016shedding, hedges2015tree}. \js{maybe also cite the phylogentics lit here? Like the speciation clock stuff.}

>>>>

If system drift induced hybrid incompatibility occurs as rapidly as our model sugests,
%even in the absence of postive Darwinian selection, 
this would imply that species originate not necessarily by means of natural selection \citep{darwin1859origin}. While the incompatibility of any one given network within an organism may be small, we note that organsisms are made up of many different networks, and that the cumulative impact of system drift across all of these may be substantial. Further, even in populations experiencing directional selection, networks underlying conserved parts of the phenotype can still experience neutral drift and harbor incompatibilities. 
Our results show that hybrids, under neutral processes, break down as a function of genetic distance, and despite the present model's myriad simplifications and assumptions, 
it may, in part, explain the observed broad patterns of reproductive isolation among diverse phyla \citep{roux2016shedding, hedges2015tree}. \js{maybe also cite the phylogentics lit here? Like the speciation clock stuff.}
